\chapter{Introduction}

\section{Background}

Helicopters are said to be the only aircrafts that, since its conception, has saved more lives then they have taken. Their  high level of mobility, vertical take off and landings and their ability to hover give helicopters great versatility. Helicopters are the most common example of a rotary aircraft and are used in environments ranging from rocky, mountainous to stormy seas. With such high stakes it is vital to minimise points of potential failure. One of these failure points is the helicopter's tail rotor. It is required to counter the toque produced by the engine which rotates the main rotor to produce lift. If the tail rotor were stop working, the helicopter would lose its controlability and would have to land immediately. A jet-tipped rotary aircraft places the propulsion on the tips of the aircraft's rotor and thus does not produce any toque that needs to be canceled, eliminating the need of a tail rotor. As the tail rotor uses the same engine, which turns the rotor, to rotate it's blades, high speed gearboxes, clutches and transmission shafts are required, which can all be omitted in a jet-tipped rotary aircraft, reducing both its weight and its complexity.

IM TRYING TO SEE IF THIS WORKS YO
%Starting from the big picture, gradually narrow focus down to this project and where this report fits in. Hello world.

\section{Objectives}

The objectives of the project (in some cases the objectives of the report). If necessary describe limitations to the scope.

\section{Motivation}

Why this specific project/report is worthwhile.